### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
Changes improving performance of F calculation (rate-limiting step)
1. vectorized calculation of mu.
2. matrix-based calc of deterministic part of growth rate

    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        # Handle special cases
        if(snap_to_grid(mu,x_grid)==0){ # 
          out[1] <- 1   
        } else {
         out <- pdfn(x_grid, mu, sigma_g)
        }
        out/sum(out)
      }))
    })

@@

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 100
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25

@@

```{r}
# Uniform pdf where width scales with mean (probably better way to do that)
# And handles degenerate/delta fn cases such as no width and zero mean
FUN <- function(P, mu, s){
  if(mu == 0){
    as.integer(P == 0)
  } else if(s > 0){
    if(mu > 0){
      dlnorm(P/mu, 0, s)
      #dunif(P, mu * (1 - s), mu * (1 + s))
    }
  }
  else { # delta spike
    P <- snap_to_grid(P, x_grid)
    mu <- snap_to_grid(mu, x_grid)
    as.numeric(as.integer(P == mu))
  }
}
pdfn <- Vectorize(FUN)
```

>>>>

    # Much faster to fill out f calls as a matrix ahead of time.  
    f_matrix <- outer(x_grid, h_grid, f, p)

    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- M[y,] %*% f_matrix %*% I[q,] 
        # Handle special cases
        if(snap_to_grid(mu,x_grid)==0){ # 
          out[1] <- 1   
        } else {
         # snap mu to grid first?  then do this by table look-up?
         out <- pdfn(x_grid, mu, sigma_g)  ## All computational time spent here.  could be done by look-up?
        }
        out/sum(out)
      }))
    })

@@

pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
xmin <- 0
xmax <- 1.5 * K
n_x <- 200
n_h <- n_x
x_grid <- seq(xmin, xmax, length = n_x)  
h_grid <- seq(xmin, xmax, length = n_h)
delta <- 0.05
xT <- 0
OptTime <- 25

@@

```{r}
# Uniform pdf where width scales with mean (probably better way to do that)
# And handles degenerate/delta fn cases such as no width and zero mean
FUN <- function(P, mu, s){
  if(mu == 0){
    as.integer(P == 0)
  } else if(s > 0){
    if(mu > 0){
      #dlnorm(P/mu, 0, s)
      dunif(P, mu * (1 - s), mu * (1 + s))
    }
  }
  else { # delta spike
    P <- snap_to_grid(P, x_grid)
    mu <- snap_to_grid(mu, x_grid)
    as.numeric(as.integer(P == mu))
  }
}
pdfn <- Vectorize(FUN)
```
